Classifier

### 2019-03-19 Paper/paper.Rmd

While there are an infinite number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost. Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above. The model has been trained on 2,500 tweets labeled 0 for "non-complaint" and 1 for "complaint." We have then tested the model on a similarly-sized dataset.

@@

Because our model uses three distinct modeling techniques, I will refer to each of these modeling techniques as "sub-models"

# The FastText Sub-Model
## Overview
In this R Markdown, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

# The PCA Sub-Model

@@

## Intro to XGBoost
XGBoost is a tool that uses gradient-boosted trees for classification. A basic understanding of decision trees and random forests is crucial to understanding gradient-boosting as well as the XGBoost package.

Decision Trees:
Decision trees are models that use a series of binary (yes/no) questions, and classify something based on the answers to those binary questions.

@@

Random Forests:

Gradient Boosting:

Links:

>>>>

While there are a massive number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost. Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above. The model has been trained on 2,500 tweets labeled 0 for "non-complaint" and 1 for "complaint." We have then tested the model on a similarly-sized dataset.

@@

Because our model uses three distinct modeling techniques, I will refer to each of these modeling techniques as "sub-models."

# The FastText Sub-Model
## Overview
In this section, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

# The PCA Sub-Model
## Intro to PCA
The idea behind PCA is that a complex multi-dimensional problem can be boiled down to a single-dimensional problem. For example, what if you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep they got, what cereal they eat for breakfast, and how many siblings they have. While all of these factors could arguably have an affect on the student's test grade, I would expect the "hours studied" and "lectures attended" variables to have the strongest correlation to test. A PCA model would notice the most important variables of a model, and simplify the model to focus on just two "principle components" (note that it still incorporates the other variables in the model, but these variables have been "simplified" or "compressed")

With a PCA model, similar results will cluster together, and clusterings can help with classification. With our student example, we would see "A" students cluster together, "B" students to cluster together, etc. While this example might seem like a simple explanation, PCA analysis can be very useful when large amounts of data are available, but you don't know which variables are most important in your classification.

For our purposes, we should be able to use PCA analysis by taking large ammounts of data we collect on tweets (their features, their average word vector, etc.) and see a clustering of complaints and non-complaints, without worrying about which features or variables of a tweet are best for classification.

## Useful Resources:
Quick Explanation of PCA: https://www.youtube.com/watch?v=HMOI_lkzW08
https://www.youtube.com/watch?v=_UVHneBUBW0

@@

## Intro to XGBoost
XGBoost is a tool that uses gradient-boosted trees for classification. A basic understanding of decision trees and random forests is crucial to understanding gradient-boosting as well as the XGBoost package. If any of these terms seem unfamiliar, I'd recommend that you look at the links I've posted below.

##### Decision Trees:
Decision trees are models that use a series of binary (yes/no) questions to classify something based on the answers to those binary questions. A decision tree can be randomly generated to model the data. This means that you could have an infinite number of trees that model the same data.

@@

##### Random Forests:
A single decision tree is not very effective for modeling--singe decision tree models have been known to overfit the data, and therefore innaccurately classify data. However, it should be noted that decision trees are more accurate at classification than a random guess, and this can make them very useful.

Random forests are models that take advantaged of the fact that a decision tree can still provide a better estimate than a random guess, despite a single tree's inaccuracy. Random forests use hundreds of decision trees (each tree randomly generated to model the same data of interest), and classify data based on the consensus of the outputs these trees.

##### Gradient Boosting:
Gradient Boosting builds on the foundation of random forests by optimizing the model. A gradient boosted random forest systematically analyzes the individual trees of a forest that perform poorly, and focuses on cleaning and improving those trees. With many iterations, a boosted model should improve significantly as it gets trained. XGBoost, the package we use for gradient boosting, is simply one popular tool of many for boosted trees.

## Useful Resources:
When I was first learning about XGBoost, I found these youtube videos to be helpful in explaining the very basic concepts behind boosted trees. Hopefully, they can help you too if you're struggling to follow along.

Decision Trees: https://www.youtube.com/watch?v=7VeUPuFGJHk
Random Forests: https://www.youtube.com/watch?v=J4Wdy0Wc_xQ
More Random Forests: https://www.youtube.com/watch?v=nyxTdL_4Q-Q
Cross Validation: https://www.youtube.com/watch?v=TIgfjmp-4BA
Boostrap Aggregating (Bagging): https://www.youtube.com/watch?v=2Mg8QD0F1dQ
MIT lecture on Boosting: https://www.youtube.com/watch?v=UHBmv7qCey4
